### 2021-04-13 manuscript/manuscript.tex
Manscrupt: Revision and First part results

%Required packages
\usepackage[utf8]{inputenc}
\usepackage{apacite}
\usepackage{caption} 
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[textwidth=160mm, textheight=210mm, hmarginratio=1:1]{geometry}
\usepackage{geometry}

@@

%Introduction section
\section{Introduction}
The topic of mental workload is a widely studied phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and cognitive neurosciences \cite{shuggi2017mental}. A commonly utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst carrying out a particular task. As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual. Workload requires to be recognized as a person-specific construct, for the amount of perceived workload ushered by a given task may vary substantially across individuals. \cite{de1996measurement}.

A commonly employed method for the assessment of workload is the well established NASA-Task Load Index questionnaire. This method inquires into the amount of perceived workload,  embodying six different dimensions \cite{hart2006nasa}. Due to practical considerations such an assessment is usually conducted post-experiment, which can in certain situations be deemed suboptimal. Consider for example an experiment, in which is aimed to assess the perceived workload of a pilot in flight. An insightful  approach towards such an experiment would be to measure the degree of perceived workload at different phases of the flight, such that can be determined which specific manoeuvres tend to embark an increase in perceived workload.  However, only after the flight is concluded, a questionnaire-based assessment such as the NASA-Task Load Index can be administrated. In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate biases. One example of such a bias is the observer-bias, which advocates that participants in an experiment tend to overexaggerate the treatment effect, i.e. the amount of perceived workload, when having to report it post-experiment \cite{mahtani2018catalogue}.

An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs to predict the degree of experienced workload.  The advantage of utilizing multiple bio-signals is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}. Doing so poses the theoretical potential of yielding a rich and multifaceted assessment of a mental construct such as workload. Additionally by taking a physiological bio-signal approach, it renders possible to train a model for each individual separately,  hereby acknowledging the between-personal differences inherent to workload, the importance of which was stressed by \citeA{de1996measurement} and touched upon in the opening paragraph of this research.

In the current research we explore the previously delineated approach to workload assessment by means of various physiological bio-signals, that is a multi-modular approach. We do so by combining data-streams stemming from three different modalities, being electroencephalography, photoplethysmography and galvanic skin response. Electroencephalography,  hereafter referred to as "EEG", is often utilized in the assessment of workload \cite{craik2019deep} and found to amongst the most adequately performing techniques within this field \cite{hogervorst2014combining}. Galvanic skin response, hereafter referred to as "GSR", equally so is a widely adopted approach towards workload investigation \cite{nourbakhsh2012using}. Lastly, heart-rate is a widely recognized indicator of workload, mostly obtained through photoplethysmography, hereafter referred to as "PPG"\cite{zhang2018evaluating}.

A deep-learning approach towards model construction is utilized. A range of four different neural networks are constructed and contrasted in performance: one of which is a multi-modular network combining all three modalities, and three of which are networks solely utilizing either the EEG, GSR or PPG modality. With this research we endeavor on the one side to explore which modalities are most adequate predictors of workload in an experimental setting, and whether a multi-modular combination of all three previously delineated modalities is preferable over the three simpler (but much less computationally demanding) single-modular models. This assessment will be propelled by model performance, but whilst taking into consideration computational costs. All networks were constructed in Python, by utilizing the deep-learning toolbox PyTorch \cite{paszke2017automatic}.

%Method section
\newpage
\section{Methods}

\subsection{Related Work} 
The following sections provide an overview of preceding research on the most optimal network architecture for each single-modular network. Subsequently, the most feasible architecture for the multi-modular framework in its entirety is explored, with particular attention placed upon the data fusion strategy and a range model optimization techniques.

\subsubsection{Electroencephalography (EEG)}
EEG constitutes a technique that detects electrical activity in the brain by using electrodes. EEG is a commonly utilized method within the field of workload assessment. An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to deal with workload specifically. With regards to these EEG applications, it was reported that studies mostly used deep belief networks and convolutional neural networks, hereafter referred to as "ConvNets". One of these approaches is advised consequently \cite{craik2019deep}.

For EEG classification, \citeA{tabar2016novel} proposed a combination of a ConvNet with a stacked auto-encoder network, hereafter referred to as "SAE network". The input layer was specified to feed into a convolutional layer with the objective of learning the filters and network parameters. The output of this convolutional layer was subsequently specified to feed into the SAE part of the network, designed to include an input layer, six hidden layers and an output layer. A classification accuracy of 90 \% was acquired with this network \cite{tabar2016novel}.

@@

\subsubsection{Galvanic Skin Response (GSR)}
GSR is a technique that measures sweat gland on the hands, hereby inferring arousal. GSR activity is known to be strongly correlated with perceived workload, indicating the utility of GSR for workload classification \cite{shi2007galvanic}.

\citeA{sun2019hybrid} explored the most suitable model design for the classification of several emotional states with GSR. Various models were explored, amongst others a support vector machine, a ConvNet and a long-short-term-memory network, hereafter referred to as "LSTM network". Additionally, the feasibility of a hybrid network, combining both the ConvNet and LSTM approaches, was explored. This aforementioned hybrid model was found to perform best, exhibiting an accuracy of 74\% \cite{sun2019hybrid}.

\citeA{dolmans2020perceived} took a multi-modular approach to workload classification, and designed a variant based on the previously delineated CovNet-LSTM approach for GSR. The performance of this model was contrasted with a network consisting solely of fully connected dense layers. Conform with findings by  \citeA{sun2019hybrid}, the hybrid model was found to perform best, displaying an accuracy of 82 \% \cite{dolmans2020perceived}. The model architecture as utilized by \citeA{dolmans2020perceived} deployed two convolutional max-pooling blocks and two LSTM layers.

\subsubsection{Photoplethysmography (PPG)}
PPG is a technique utilized to measure volumetric changes in blood peripheral circulation, from which it is possible to derive heart-rate. \citeA{zhang2018evaluating} contrasted several approaches towards workload classification, each utilizing a different modality. PPG was found to perform among the best, explaining why PPG constitutes one of the most widely utilized modalities in workload classification.

Work by \citeA{biswas2019cornet} explored a deep-learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information. Exceptional results were realized with a deep neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}. This performance was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed by two LSTM layers.

\subsubsection{Multi-modular Fusion Strategy}  
When conducting a multi-modular deep-learning approach, the information streams stemming from the three modalities are required to be combined, i.e. "fused", at a certain point in the network, in order to ultimately result in a single classification of workload. Fusion can be done conforming different strategies. Several strategies as proposed by \citeA{ramachandram2017deep} have been considered.

Early, or data-level, fusion constitutes an approach that fuses data sources before being fed into the network. Techniques that manage this include for example principle-component analysis and factor analysis. Early fusing is usually proven to be quite challenging, residing in the fact that data streams stemming from different modalities often differ in dimensionality and sampling rate. In addition, when taking an early fusion approach, the oversimplified assumption of conditional independence is made implicitly. This assumption is unrealistic in nature, for data stemming from different modalities are expected to be correlated in practice \cite{ramachandram2017deep}.

Late, or decision-level, fusion refers to the process of aggregating the decisions of multiple separate networks, each applied towards every modality separately. In case the data sources stemming from the various modalities are either correlated or ultimately differ in their dimensionality, late fusion is a much more feasible approach as contrasted with early fusion \cite{ramachandram2017deep}.

Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modular deep-learning problems. Data streams are usually fused by a concatenation layer, joining the outputs of the separately defined network parts of each modality. This results in a single joint deep neural network. Classification is managed based on the outputs from each of the single-modular network parts. Several "higher-order layers" are usually defined in between the concatenation layer and the ultimate classification. The depth of the fusion, i.e. the specified number of higher-order layers, can be chosen conform to the specific circumstances, posing intermediate fusion to be the most flexible and therefore the most widely adopted fusion strategy \cite{ramachandram2017deep}.

Indeed, when consulting the literature, one is forced to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep-learning approaches. When taking an intermediate fusion approach, the higher-order part of the network needs to be designed and established, for which several previous research endeavors are considered.  \citeA{rastgoo2019automatic} utilized a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers, two dense layers and a softmax layer. A simpler approach is adopted by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers, and ending with a soft-max layer. Lastly, \citeA{dolmans2020perceived} took a relatively deep intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.

\subsubsection{Model Optimization Strategies}
The technique of batch normalization was originally proposed by \citeA{ioffe2015batch}, and is often a applied in deep-learning with the objective of stabilizing a network. Especially ConvNets are able to capitalize on this technique. It is beneficial to include a batch normalization layer after each convolutional layer, re-centering and re-scaling the input feeding into subsequent layers. When incorporating a batch normalization layer, it is recommended to do so before the specification of the activation function \cite{ioffe2015batch}. An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived} and \citeA{schirrmeister2017deep} through specifying a batch normalization layer following each convolutional layer. Equally so, the best performing network for PPG as proposed by \citeA{biswas2019cornet} included a batch normalization layer succeeding each convolutional layer.

Pooling layers are commonly employed in ConvNets, usually succeeding a convolutional layer with the purpose of decreasing the dimensionality. The objective of such layers are to merge similar features into one. For a more extensive elaboration on pooling, please consult \citeA{lecun2015deep}. In their EEG ConvNets, both \citeA{schirrmeister2017deep} and \citeA{tabar2016novel} specified a max-pooling layer after each convolutional layer. The network as proposed for GSR by \citeA{sun2019hybrid} incorporated a max-pooling layer after each but one of the convolutional layers. Lastly, the network as proposed for PPG by \cite{biswas2019cornet} specified a max pooling layer after each convolutional layer.

Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be utilized to optimize hyper-parameters such as learning rate and dropout. Substantial advancements in deep-learning have been attained by utilizing HPO, especially for ConvNets \cite{bergstra2012random}. The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled and optimization can be performed \cite{akiba2019optuna}. 
\bigskip

\subsection{Data}
The subsequent section will provide an overview of the utilized data. Attention is primarily placed upon the experimental setup, the description of the respondents, the utilized devices for data collection and the synchronization process.

\subsubsection{Experimental Setup}
The experimental setting in which the data collection took place is the open-source spaceship video-game Empty Epsilon, in which respondents were asked to carry out tasks on a virtual spaceship \cite{daid2016empty}. This experiment was instituted by the Brain Computer Interfaces testbed, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo. The experiment constituted three different segments, in each of which the respondent had to carry out tasks. These tasks were designed to evoke varying degrees of workload. Each segment consisted of six small sessions lasting roughly five to ten minutes. These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment. Within each segment, the order in which the sessions were presented was randomized. The order in which the three main segments were administrated was not randomized. Between every three sessions, respondents were given a short two minute break. A schematic overview of the experimental structure is depicted as Figure \ref{fig:experimental}.

After each of the 18 sessions, respondents were asked to fill in the TLX questionnaire, compromising of six questions each. This resulted in 18 filled in questionnaires per respondent. Each questionnaire inquired upon the degree to which the respondent experienced workload during the preceding session. These measurements have been utilized to label the data for network training purposes.

\begin{figure}
\caption{Experimental Setup}
\bigskip
\includegraphics[scale=0.4]{experimental_setup}
\label{fig:experimental}
\end{figure}

The first segment emulated a scenario in which hostile spaceships approached the respondent's spaceship. The respondent was required to quickly react by defusing the hostiles in order to survive. The increment in difficulty caused the process of defusing hostile spaceships to become more challenging, hereby aiming to cause an increase in workload. The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible. Obstacles around which the respondent had to navigate carefully, as well as hostile spaceships the respondent had to decimate, were introduced in the higher difficulty sessions. The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests. In the increased difficulty settings, variables that could overheat the spaceship were introduced, demanding the respondent to multi-task and aiming to increase workload as a consequence.

\subsubsection{Respondents}
In total, 38 respondents have participated in the study. Demographic information of the respondents is set forth in Table \ref{table:demographics}. The respondents are students recruited from the University of Twente. Recruitment has been conducted by means of Sona, which is a cloud-based participant management system. A requirement for participation was that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker. This was assessed by means of a short demographic questionnaire prior to the experiment. Additionally, respondents were made aware of informed consent prior to the experiment in order to ensure completely voluntary participation. Respondents were able to draw back from the experiment at any time.

\bgroup
\def\arraystretch{1.6}  
\begin{table}[h]
\bigskip
\caption{Demographic Overview Respondents}
\label{table:demographics}
\begin{tabular}{rrrr}
  \hline
 & Female & Male \\ 
  \hline
10-19 &   7 &   0 &  \hspace{1cm} \\ 
  20-29 &  13 &   4 &   \\ 
  30-39 &   1 &   1  &   \\ 
  40-49 &   0 &   8  &   \\ 
  50-59 &   0 &   0 &   \\ 
  60-69 &   0 &   4 &   \\ \hline
  Total    &  21 &  17 & \\ \hline
\end{tabular}
\end{table}
\egroup

\subsubsection{Devices and Sampling Rate}
The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements. This device was worn on the wrist. Signals were communicated wirelessly. An ear-clip was utilized for measuring PPG, and converting this to estimate heart rate. Skin conductivity, or GSR, was monitored by two electrodes attached to the fingers \cite{shimmer}. EEG measurement was conducted with the Muse 2, which is a multi-sensor headband that provides feedback on brain activity \cite{muse}. The Shimmer3 GSR+ is able to read and output data signals on a sampling rate of 256 Hz, whereas the Muse 2 is able to sample at a maximum rate of 220 Hz.

As was set forth in the introduction, real-time classification requires a swiftly classifying network. A higher sampling rate equals more data traveling through the network, decelerating classification speed. As a consequence, it is highly beneficial to input data on the minimum required sampling rate with which key features can be detected consistently.

>>>>

%Required packages
\usepackage[utf8]{inputenc}
\usepackage{apacite}
\usepackage{caption} 
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[textwidth=160mm, textheight=210mm, hmarginratio=1:1]{geometry}
\usepackage{geometry}
\usepackage[capposition=top]{floatrow}

@@

%Introduction section
\section{Introduction}
The topic of mental workload is a widely studied phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and cognitive neurosciences \cite{shuggi2017mental}. A commonly utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon one whilst one carries out a particular task. As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual. Workload, however, requires to be recognized as a person-specific construct, for the amount of perceived workload ushered by a given task may vary substantially across individuals. \cite{de1996measurement}.

A commonly employed method for the assessment of workload is the well established NASA-Task Load Index questionnaire, hereafter referred to as "NASA-TLX". This method inquires into the amount of perceived workload,  embodying six different dimensions \cite{hart2006nasa}. Due to practical considerations such an assessment is usually conducted post-experiment, which can in certain situations be deemed suboptimal. Consider for example an experiment in which it is aimed to assess the perceived workload of a pilot in flight. An insightful  approach towards such an experiment would be to measure the degree of perceived workload during different phases of the flight, such that can be determined which specific manoeuvres tend to cause an increase in perceived workload.  However,  a questionnaire-based assessment such as the NASA-TLX can only be administrated after the flight is concluded. In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate biases. One example of such a bias is the observer-bias, dictating that participants of an experiment tend to overexaggerate the treatment effect, i.e. the amount of perceived workload in our case, when having to report it post-experiment \cite{mahtani2018catalogue}.

An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs to predict the degree of experienced workload.  A considerable advantage of such an approach is that it renders possible to cater the method towards the individual,  hereby acknowledging the between-personal perceptual differences inherent to workload, the importance of which was discussed in the first paragraph of this paper and stressed by \citeA{de1996measurement}. But taking a physiological bio-signal-approach poses more advantages: e.g. one may utilize multiple complementary bio-signals, each stemming from a different physiological source simultaneously \cite{ramachandram2017deep}. Doing so poses the theoretical potential of yielding a rich and multifaceted assessment of a mental construct such as workload. In addition, with such an approach one may select a variety of the most suitable physiological bio-signals, hereafter referred to as "modalities",  and combine these information streams in order to yield a multifaceted prediction.

With the current research endeavor we explore the feasibility of an approach to workload assessment by means of multiple modalities simultaneously, hereafter referred to as "multi-modular approach". We do so by combining data-streams stemming from three different modalities, being electroencephalography, photoplethysmography and galvanic skin response. Electroencephalography,  hereafter referred to as "EEG", is often utilized in the assessment of workload \cite{craik2019deep} \cite{berka2005evaluation} and found to be amongst the most adequately performing techniques within the field \cite{hogervorst2014combining}. Galvanic skin response, hereafter referred to as "GSR", equally so is a widely adopted approach towards workload assessment \cite{nourbakhsh2012using} \cite{zhou2015dynamic}. Lastly, heart-rate is a widely recognized indicator of workload, mostly obtained through photoplethysmography, hereafter referred to as "PPG" \cite{zhang2018evaluating} \cite{jimenez2018using}.

A deep learning approach towards modeling is adopted. A range of four different deep neural networks, hereafter referred to as "DNN's", are constructed and contrasted in performance: three of which are single-modular DNN's, i.e. networks each utilizing data from only a single modality. Thus,  one DNN solely utilizes the EEG modality,  one solely utilizes GSR and one solely utilizes PPG. The fourth network is a multi-modular network combining all three modalities into one. With this research we firstly sought to explore which modalities constitute the most adequate predictors of workload in an experimental setting, and secondly whether a multi-modular combination is preferable over the three simpler (but much less computationally demanding) single-modular DNN's. This assessment will be propelled by contrasting network performance, however when drawing conclusions, considerations regarding computational costs will be taken into consideration as well. All networks were constructed in Python, by utilizing the deep-learning toolbox PyTorch \cite{paszke2017automatic}.

%Method section
\newpage
\section{Data \& Methods}

\subsection{Data}
The subsequent section will provide an overview of the utilized data. Attention is placed upon the experimental setup, the description of the respondents, the utilized devices for data collection and the synchronization process.

\subsubsection{Experimental Setup}
The experimental setting in which data collection befell is the open-source spaceship video-game Empty Epsilon, in which partakers carry out tasks on a virtual spaceship bridge \cite{daid2016empty}. This experiment was instituted by the Brain Computer Interfaces testbed, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo. The experiment constituted three different segments, in each of which the respondent had to carry out tasks. These tasks were designed to evoke varying degrees of workload. Each segment consisted of six small sessions, lasting roughly five to ten minutes. These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment. Within each segment, the order in which the sessions were presented was randomized. Between every three sessions, respondents were given a short two minute break. A schematic overview of the experimental structure is depicted as Figure \ref{fig:experimental}.

After each of the 18 sessions, respondents were asked to fill out the NASA-TLX, resulting in 18 filled in questionnaires per respondent. Each questionnaire consists out of 6 questions, inquiring upon the degree to which the respondent experienced workload during the preceding session. The mean of a subset of four of these items have been utilized to label the data for training purposes.  Two items were not incorporated into the scale, for they inquired into physical demand specifically, which given the experiment took place on a computer whilst sitting behind a desk was considered to be a redundant factor. Each item, and hence the newly constructed scale, ranges from 0-20, wherein 0 reflects low workload and 20 reflects high workload.  In order to encourage numerical stability, label scores were normalized to reside in-between 0-1.

\begin{figure}
\caption{Schematic Depiction of the Experimental Setup}
\bigskip
\includegraphics[scale=0.35]{experimental_setup}
\label{fig:experimental}
\bigskip
\end{figure}

The first segment emulated a scenario in which hostile spaceships approached the respondent's spaceship. The respondent was required to quickly respond by defusing the hostiles in order to survive. The increment in difficulty caused the process of defusing hostile spaceships to become more challenging, hereby aiming to cause an increase in workload. The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible. Obstacles around which the respondent had to navigate carefully, as well as hostile spaceships the respondent had to decimate, were introduced in the higher difficulty sessions. The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests. In the increased difficulty settings, variables that could overheat the spaceship were introduced, demanding the respondent to multi-task and aiming to increase workload as a consequence.

\subsubsection{Participants}
After having to omit 7 participants due to hardware failure, 27 respondents were included in the final analysis.  18 participants are female whereas 9 are male. The mean age and standard deviation are $\mu =26, \sigma = 10.31$ respectively. The participants are students recruited from the University of Twente, as well as several employees of Thales group Hengelo.

\subsubsection{Devices and Synchronization}
The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements. This device is worn on the wrist. Signals are communicated wirelessly via Bluetooth. An ear-clip is utilized for measuring PPG. The Shimmer3 GSR+ automatically converts measured PPG signals to heart-rate. Skin conductivity, or GSR, is measured by two electrodes attached to the fingers \cite{shimmer}. EEG measurement was conducted with the Muse 2, which is a commercially offered multi-sensor headband that provides feedback on brain activity \cite{muse}. The Muse 2 headband constitutes five sensors, each monitoring a different brainwave frequency.

The Shimmer3 GSR+ measures signals on a sampling rate of 256 Hz, whereas the Muse 2 measures at a sampling rate of 220 Hz. Given that multiple devices are utilized, data streams are required to be properly synchronized. This was accomplished by means of an application called Lab-Streaming Layer, hereafter referred to as "LSL", developed by \citeA{kothe2018lab}. The three data streams stemming from the two devices were all streamed to LSL during the experiment. LSL subsequently properly synchronizes all data streams in real-time,  such that they are parallel, hence all referring to equivalent points in time.

\subsection{Related Work} 
The following section provides an overview of preceding research regarding the assessment of workload by means of physiological bio-signals, with a focus on deep learning approaches. Attention is predominantly placed upon the most feasible network architectures, in addition to a range of model optimization techniques and to the data fusion strategy for the multi-modular DNN. The final part of this section will be dedicated to hyperparameter optimization.

\subsubsection{Electroencephalography (EEG)}
An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all publications to consider workload assessment specifically. The lion's share of these publications utilized either a deep belief networks or convolutional neural network, hereafter referred to as "ConvNet". One of these approaches is encouraged by the authors consequently \cite{craik2019deep}.

\citeA{tabar2016novel} proposed a hybrid of a ConvNet with a stacked auto-encoder network, hereafter referred to as "SAE network". Inputs were specified to feed into the convolutional-part with the objective of learning extracting features. The output of this part was subsequently specified to feed into the SAE part of the network,  which encompasses a stack of dense-layers, designed specifically as an input layer, six hidden layers and an output layer. A classification accuracy of 90 \% was acquired with this network \cite{tabar2016novel}.

@@

\subsubsection{Galvanic Skin Response (GSR)}
\citeA{sun2019hybrid} explored the most suitable approach to the classification of several emotional states with GSR. Various models were explored, amongst others a support vector machine, a ConvNet and a long-short-term-memory, hereafter referred to as "LSTM", network. Additionally, the feasibility of a hybrid DNN, combining both the ConvNet and LSTM approaches, was explored. This aforementioned hybrid model was found to perform best, exhibiting an accuracy of 74\% \cite{sun2019hybrid}.

\citeA{dolmans2020perceived} took, amongst other approaches to workload prediction,  a GSR approach, and designed a variant based on the previously delineated CovNet-LSTM structure. The performance of this model was contrasted with a network consisting solely of fully connected dense layers. Conform with findings by  \citeA{sun2019hybrid}, the hybrid model was found to perform best, displaying an absolute difference between predicted and true label of 0.197 (scaled on 0-1). The model architecture as utilized deployed two convolutional max-pooling blocks and two LSTM layers \cite{dolmans2020perceived}.

\subsubsection{Photoplethysmography (PPG)}
Research by \citeA{biswas2019cornet} explored a deep learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information. Exceptional results were realized with a DNN, attaining an average accuracy of 96 \% \cite{biswas2019cornet}. This performance was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed by two LSTM layers.

\subsubsection{Multi-modular Fusion Strategy}  
When conducting a multi-modular deep learning approach,  information streams stemming from the different modalities are required to be combined, i.e. "fused", at a certain point in the network in order to ultimately result in a single prediction of workload. Fusion can be done conforming several strategies. Three strategies as proposed by \citeA{ramachandram2017deep} have been considered.

Early, or data-level, fusion constitutes an approach that fuses data sources before being fed into the network. Early fusing is usually proven to be quite challenging, residing in the fact that data streams stemming from different modalities often differ in their dimensionality and sampling rate. In addition, when taking an early fusion approach, the oversimplified assumption of conditional independence is made implicitly. This assumption is unrealistic in nature, for data stemming from different modalities are expected to be correlated in practice \cite{ramachandram2017deep}.

Late, or decision-level, fusion refers to the process of aggregating the decisions of multiple separate networks, each applied towards every modality separately. In case the data sources stemming from the various modalities are either correlated or ultimately differ in their dimensionality, late fusion is often a more feasible approach as opposed to early fusion \cite{ramachandram2017deep}.

Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modular deep-learning problems. Data streams are usually fused by a concatenation layer, joining the outputs of the separately defined network parts of each modality. This results in a single joint deep neural network. Several "higher-order layers" are usually defined in between the concatenation layer and the ultimate classification. The depth of the fusion, i.e. the specified number of higher-order layers, can be chosen conform to the specific circumstances, posing intermediate fusion to be the most flexible and therefore the most widely adopted fusion strategy \cite{ramachandram2017deep}.

Indeed, when consulting the literature, one is prone to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep learning approaches. When taking an intermediate fusion approach, the higher-order part of the network needs to be designed and established, for which several previous research endeavors are considered.  \citeA{rastgoo2019automatic} utilized a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers and two dense layers. A simpler approach is adopted by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers. Lastly, \citeA{dolmans2020perceived} took a relatively deep intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.

\subsubsection{Model Optimization Strategies}
The technique of batch normalization was initialized by \citeA{ioffe2015batch}, and is widely utilized in DNN's with the objective of stabilization. Especially ConvNets benefit from this technique. It is beneficial to incorporate a batch normalization layer subsequent to a convolutional layer, but before feeding into the activation function \cite{ioffe2015batch}.  All previously delineated networks architectures utilize batch normalization layers, in most cases specified subsequent to each convolutional layer \cite{dolmans2020perceived} \cite{tabar2016novel} \cite{schirrmeister2017deep} \cite{biswas2019cornet} \cite{sun2019hybrid}.

Pooling layers are commonly employed in ConvNets, usually succeeding a convolutional layer with the purpose of reducing dimensionality. The objective of such layers are to down-sample features into a more compact space, hereby only retaining indispensable information. For a more extensive elaboration on pooling, please consult \citeA{lecun2015deep}. All previously delineated networks architectures utilize max-pooling layers, usually specified subsequent to the activation layer \cite{dolmans2020perceived} \cite{tabar2016novel} \cite{schirrmeister2017deep} \cite{biswas2019cornet} \cite{sun2019hybrid}.

\subsubsection{Hyper Parameter Optimization}
Hyper parameter optimization, hereafter referred to as "HPO", is a technique that can be utilized to optimize network hyper-parameters, such as learning rate and dropout rate.  In theory, one could optimize the entire DNN architecture, including the number of neurons/filters in (convolutional) layers, the number of layers in general, whether to use certain layers etc. There is, however, a strong relationship between the amount of parameters to be optimized and the computational resources required to do so, in where many parameters to optimize tends to inflate computational costs by a substantial amount. Substantial advancements in DNN performance have been attained by utilizing HPO, especially for ConvNets \cite{bergstra2012random}. The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled and optimization can be performed \cite{akiba2019optuna}. 
\bigskip

\subsection{Deep Neural Network Architectures \& Training} \label{section:DNN}
Before elaborating on the chosen DNN architectures, we will firstly touch upon several universal truths for all networks.  Given the person-specific character inherent to physiological data,  networks for each respondent have been trained independently. Despite this, all network architectures across persons are similar, except for the specified hyperparamaters: these were optimized for each of the four networks and for each respondents individually as well. As a consequence, four DNN's are trained for each of the 27 respondents separately, resulting in a total of 108 trained networks, each one utilizing one of 108 sets of optimized hyperparamaters. All networks were

\subsubsection{Single-modular Network}
All single-modular network architectures took inspiration from previously delineated research \cite{schirrmeister2017deep} \cite{dolmans2020perceived} \cite{sun2019hybrid} \cite{biswas2019cornet}. In contrast with most of these previous endeavors, we opted for a ConvNet-only approach, i.e. without LSTM-layers, for the objective of the current research is not of a time-series-forecasting-kind. An experimental scenario wherein the course of actions over the duration of the experiment always unfold in a similar manner are inclined to benefit from acknowledging this time-series-like nature, hence benefiting from LSTM. An example of such a scenario would be a pilot in flight: whilst workload arousing phenomena that occur during a flight could differ across takes, the general chronological structure of the scenario always adheres to a similar blueprint. I.e., starting with ascend, likely to arouse a peak in workload, and closing with touch down, equally so likely to arouse a peak in workload. Our experimental scenario doesn't adhere to such a set in stone unfolding, for the order in which the scenario's with variable difficulty were presented was entirely randomized.  Hence, for there is no chronologically consistent development of the experimental scenario, we opted for a ConvNet approach without opting to learn from the development over time, thus without LSTM-layers.

The three single-modular DNN architectures are depicted alongside one another as Figure \ref{fig:singlearchitecture}. Each of the single-modular networks can be distinguished by two separate part, being the convolutional part and the prediction part.  The objective of the convolutional part is to extract features from the data. For each network, this part consists of four convolutional blocks, each compromising a convolutional layer, a batch normalization layer, the Exponential Linear Unit, hereafter referred to as "ELU", activation function, and a max-pooling layer respectively. The prediction part compromises a flatten-layer,  with the objective of representing all input into one dimensional shape, followed by a dropout layer, a dense layer, a Rectified linear activation, hereafter referred to as "RELU", closed by another dense layer. An overview of the amount of utilized filters / neurons for each layer of each network is provided in Table \ref{table:modelvariations}.

Consistent with training, HPO was equally so done for each respondent individually, resulting in 27 optimized sets of parameters for the EEG networks, 27 for the PPG networks and 27 for the GSR networks.We optimized the learning rate, dropout rate and the amount of neurons for the first dense layer in 50 trials per network.  For training, a total of 600 epochs have been made through the data for each network independently. All training and HPO of the single-modular networks has been done on a V100 GPU,  offered by the GPU cloud service Google Collab.  Total running time for the single-modular networks was about four days, the most of which was absorbed by HPO.

\newgeometry{margin=2cm}
\begin{figure}
\caption{The Three Single-modular Network Architectures}
\bigskip
\includegraphics[scale=0.7]{single_model_architecture}
\label{fig:singlearchitecture}
\floatfoot{\emph{Note:} Each network constitutes a convolutional part of four convolutional blocks, and a classification part of two fully connected dense layers. }
\end{figure}
\restoregeometry

\newgeometry{margin=1.6cm}
\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\caption{Network Sizes}
\label{table:modelvariations}
\begin{tabular}{lllll}
\hline
        & EEG-Net/Part  & GSR-Net/Part  & PPG-Net/Part  & Multi-Modular Head-Net     \\ \hline
 Single-Modular-Nets & Dense Out: 1 & Dense Out: 1 & Dense Out: 1 &   \\
        & Dense 1: \emph{hpo} & Dense 1: \emph{hpo} & Dense 1: \emph{hpo} &   \\
        \vspace{1.5ex}        
        & Drop out: \emph{hpo} & Drop out: \emph{hpo} & Drop out: \emph{hpo} &   \\
        & Conv4: 200 & Conv4: 128 & Conv4: 128 &    \\ 
        & Conv3: 100 & Conv3: 64 & Conv3: 64 &    \\ 
        & Conv2 50 & Conv2: 32 & Conv2: 32 &    \\ 
        \vspace{3ex}
        & Conv1: 25 & Conv1: 16 & Conv1: 16 &  \\         
  Multi-Modular-Net & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense Out: 1  \\
        & Conv4: 200 & Conv4: 128 & Conv4: 128  &  Dense 3: \emph{hpo} \\ 
        & Conv3: 100 & Conv3: 64 & Conv3: 64 & Dense 2: \emph{hpo}  \\ 
        & Conv2 50 & Conv2: 32 & Conv2: 32 & Drop out: \emph{hpo}    \\ 
        \vspace{3ex}
        & Conv1: 25 & Conv1: 16 & Conv1: 16 &    \\   \hline
\end{tabular}
\vspace{2ex}
\begin{doublespacing}

\floatfoot{\textit{Notes:} For all convolutional layers the depicted number reflects the amount of utilized filters, whereas for dense layers it reflects the amount  of nodes.  All depicted values are the amount of filters/nodes that a respective layer outputs. \textit{input} refers to fully connected dense layers, wherein the number of outputting nodes equals the number of inputting nodes. \textit{Hpo} implies that the value for the respective layer was optimized (see first paragraph of section \ref{section:DNN})}

\end{doublespacing}
\end{table}
\egroup
\restoregeometry
